\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em} %1em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newenvironment{bibsection}%
        {\begin{enumerate}{}{%
%        {\begin{list}{}{%
       \setlength{\leftmargin}{\bibhang}%
       \setlength{\itemindent}{-\leftmargin}%
       \setlength{\itemsep}{\bibsep}%
       \setlength{\parsep}{\z@}%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{enumerate}\vspace{-.6\baselineskip}}
%        {\end{list}\vspace{-.6\baselineskip}}
\makeatother
\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Amit Sarker} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 

\moveleft.5\hoffset\centerline{Phone No. : +880 1521211137}
\moveleft.5\hoffset\centerline{Email : amitcsedu99@gmail.com}
LinkedIn : \href{https://www.linkedin.com/in/amit-sarker99/}\\
GitHub : \href{https://github.com/amit-sarker}\\
Website : \href{https://amit-sarker.github.io/}
%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	Interests
%----------------------------------------------------------------------------------------
 
\section{INTERESTS}  
Artificial Intelligence, Multi-agent Coordination and Optimization, Multi-agent Planning and Scheduling, Interaction Between Human and Robot/AI.

%----------------------------------------------------------------------------------------
%	Education 
%----------------------------------------------------------------------------------------
\section{EDUCATION} 
{\sl \bf{University of Dhaka}} \hfill 2020 \\ Bachelor of Science in Computer Science and Engineering \\
CGPA Score - 3.77/4.00

% {\sl \bf{Dhaka Residential Model College}} \hfill 2012\\ Higher Secondary School Certificate\\
% GPA Score - 5.00/5.00

% {\sl \bf{Mohangonj Pilot Govt. High School}} \hfill 2010\\ Secondary School Certificate\\
% GPA Score - 5.00/5.00 

%----------------------------------------------------------------------------------------
%	Training and Internships 
%----------------------------------------------------------------------------------------

\section{EXPERIENCE}
{\sl \bf{TigerIT Bangladesh LTD.}}\hfill Apr. 2020 - Present\\
Full Stack Software Engineer \\
Software Quality Assurance (SQA) team \\
Led By : Al Mamun Chowdhury

{\sl \bf{Cognitive Agents and Interaction Lab (CAIL)}}\hfill Nov. 2018 - Jan. 2020\\
Research Student, University of Dhaka \\
Search-Based algorithm to solve Continuous DCOPs \\
Supervised by : Dr. Md. Mosaddek Khan

% Embedded Systems and its Applications
%----------------------------------------------------------------------------------------
%	Technical Skills 
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	Awards 
%---------------------------------------------------------------------------------------

\section{AWARDS}

{\sl \bf{Code Samurai 2019 -- Inter University Hackathon} } \hfill Nov. 2019 \\ 
\textbf{1st Runner-up} \\
It was a national-level competition jointly organized by BJIT Limited, BJIT Academy and Department of CSE, University of Dhaka.


\section{PUBLICATIONS}
\begin{bibsection}
\item \textbf{Amit Sarker}, Abdullahil Baki Arif, Moumita Choudhury, and Md. Mosaddek Khan. C-CoCoA: A Continuous Cooperative Constraint Approximation Algorithm to Solve Functional DCOPs. In \emph{Proc. of the 19th International Conference on Autonomous Agents and Multiagent Systems \textbf{(AAMAS 2020)}.} (Extended Abstract). \\ 
\emph{11th International Workshop on Optimization and Learning in Multiagent Systems \textbf{(OptLearnMAS)} @ \mbox{AAMAS}, 2020} (Full Paper).

\item Moumita Choudhury, \textbf{Amit Sarker}, Md. Mosaddek Khan, and William Yeoh. A Particle Swarm Inspired Approach for Continuous Distributed Constraint Optimization Problems. \emph{arXiv:2010.10192  (under review), 2020}.

\item \textbf{Amit Sarker}, Abdullahil Baki Arif, and Md. Mosaddek Khan. Applying Local Search Algorithms for solving Functional Distributed Constraint Optimization problems
(F-DCOPs) in Multi-Agent Systems. \emph{Undergraduate Thesis, Computer Science and Engineering, University of Dhaka, 2019}.
\end{bibsection}



\section{TECHNICAL \\ SKILLS} 

{\sl Programming Languages:} Python, C/C++, LaTeX. \\
{\sl Databases:}  MySQL, Oracle, MongoDB. \\
{\sl Libraries:} PyTorch, Pandas, NumPy, Matplotlib. \\
{\sl Web Technologies:} JavaScript, Python Flask, HTML/CSS. \\
{\sl Cloud Platform:} Google Firebase.


%----------------------------------------------------------------------------------------
%	Projects 
%----------------------------------------------------------------------------------------

\section{PROJECTS}
- {My Food Diary}
{\sl \hfill {\normalfont Feb. 2018 - Apr. 2018} 
\begin{itemize}
    \item An android app implemented in Java for food tracking and health management. A user-friendly way to track daily calorie intake, water consumption and weight.
    \item Genetic algorithm based automated food suggestions and goal oriented motivations.
\end{itemize}
}

- {Track Me}
{\sl \hfill {\normalfont Jul. 2017 - Oct. 2017} 
\begin{itemize}
    \item An android app implemented in Java for tracking personal vehicles on road by using Google Maps API.
    \item Clustering based approach to detect anomaly in driving pattern and notify the car owner.
\end{itemize}
}

- {GRE\_WebApp}
{\sl \hfill {\normalfont Jul. 2018 - Oct. 2018} 
\begin{itemize}
    \item Flash-card based web application for the students to take preparation for the GRE (Graduate Record Examination).
    \item The backend is developed using Python (Flask framework), MongoDB and the frontend is developed using HTML, CSS, Javascript.
\end{itemize}
}

- {CSEDU Book Club}
{\sl \hfill {\normalfont Feb. 2019 - Apr. 2019} 
\begin{itemize}
    \item An application for maintaining the book sharing activities of CSEDU Book Club.
    \item Android app is implemented in Java, Web app is implemented in Python (Flask framework), Firebase database is used for both versions.
\end{itemize}
}

- {29 Card Game}
{\sl \hfill {\normalfont Feb. 2017 - Apr. 2017} 
\begin{itemize}
    \item A four-player 29 card game that is implemented by using Java Socket Programming.
\end{itemize}
}

- {Stick Hero}
{\sl \hfill {\normalfont Jun. 2016 - Aug. 2016} 
\begin{itemize}
    \item Windows version of the famous stick hero game. Implemented by using C++ and Simple and Fast Multimedia Library (SFML).
\end{itemize}
}


\section{REFERENCE}

{\sl {\bf Dr. Md. Mosaddek Khan } \\ Assistant Professor, Department of Computer Science and Engineering \\ University of Dhaka
\\ Email - mosaddek@du.ac.bd}


\end{resume}
\end{document}
